Discussion Draft v1

### 2020-04-16 doc/Discussion.rmd
small changes

---
title: ""
date: ''
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
    toc_float: yes
  pdf_document: default
  word_document:
    toc: yes
    toc_depth: '3'
bibliography: refs_Main_Report.bib
---

>>>>

---
title: ''
date: ''
output:
  word_document:
    toc: yes
    toc_depth: '3'
  pdf_document: default
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
    toc_float: yes
bibliography: refs_Main_Report.bib
---
